Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-06 submission.tex
minor changes to sec:setup

\paragraph{Parser}
In choosing a syntactic parser for our experiments, we considered previous work
on dependency parsing of Norwegian, specifically that of
\newcite{Sol:Skj:Ovr:14}, who found the Mate parser \cite{Boh:10} to have
the best performance for parsing of NDT. Furthermore, recent dependency
parser comparisons \cite{Cho:Tet:Ste:15} showed that Mate performed very well
on parsing of English, outperforming a range of contemporary state-of-the-art
parsers. We will be using Mate for gauging the effect of the tag set modifications in
our experiments.

@@

% fixme: tror nok dette bør flyttes og kortes ned. kan bakes inn med det som
% står under "Tag Set Mapping".
Our approach is somewhat semi-automatic in that we employ a "hybrid"
combination of manual annotation and automatic labeling in our experiments. Our
initial tags are gold standard, and using linguistic insight coupled with
computational considerations, we introduce new gold standard distinctions to
the tag set. The data sets with these tags are run through a pipeline with
automatically assigned tags in both training and testing, where the most
promising modifications are used "further". Hence, the tag set modifications
are not deterministic, nor do we try all possible combination; we only
experiment with linguistically motivated distinctions. We are in reality
altering the gold standard tags by the addition of more linguistic information.

@@

\subsection{Tag Set Experiments}
We modified the tags for nouns (\texttt{subst}), verbs (\texttt{verb}),
adjectives (\texttt{adj}), determiners (\texttt{det}) and pronouns
(\texttt{pron}) in NDT by appending selected sets of morphological features to
each tag in order to increase the linguistic information expressed by the tags.
For each tag, we first experimented with each of the available features in
isolation before employing various combinations of them. We based our choices
of combinations on how promising the features are and what we deem worth
investigating in terms of linguistic utility, in order to see how the features
might interact.

>>>>

\paragraph{Parser}
In choosing a syntactic parser for our experiments, we considered previous work
on dependency parsing of Norwegian, specifically that of
\newcite{Sol:Skj:Ovr:14}, who found the Mate parser \cite{Boh:10} to have the
best performance for parsing of NDT. Furthermore, recent dependency parser
comparisons \cite{Cho:Tet:Ste:15} showed that Mate performed very well on
parsing of English, outperforming a range of contemporary state-of-the-art
parsers. We will be using Mate for gauging the effects of the tag set
modifications in our experiments.

@@

% fixme: tror nok dette bør flyttes og kortes ned. kan bakes inn med det som
% står under "Tag Set Mapping".
Our approach is somewhat semi-automatic in that we employ a "hybrid"
combination of manual annotation and automatic labeling in our experiments. Our
initial tags are gold standard, and using linguistic insight coupled with
computational considerations, we introduce new gold standard distinctions to
the tag set. The data sets with these tags are run through a pipeline with
automatically assigned tags in both training and testing, where the most
promising modifications are used "further". Hence, the tag set modifications
are not deterministic, nor do we try all possible combination; we only
experiment with linguistically motivated distinctions.

@@

\subsection{Tag Set Experiments}
We modified the tags for nouns (\texttt{subst}), verbs (\texttt{verb}),
adjectives (\texttt{adj}), determiners (\texttt{det}) and pronouns
(\texttt{pron}) in NDT by appending selected sets of morphological features to
each tag in order to increase the linguistic information expressed by the tags.
For each tag, we first experimented with each of the available features in
isolation before employing various combinations of them. We base our choices
of combinations on how promising the features are and what we deem worth
investigating in terms of linguistic utility, in order to see how the features
might interact.
